### 2016-11-16 conclusion.tex
Added context section to conclusion

\section{Results in Context}
Developing a versatile, accurate, resolution insensitve model for feedback has
been a challenge in galaxy simulations for decades.  While a number of recent
models have been developed that are able to produce galaxies which match some
observables, all of these models have relied on purely numerical features to
enhance the effectiveness of feedback and counter the effects of limited
resolution.  The \citet{Keller2014} presented in Chapter 2 is the first model of
its kind that uses a first-principles approach to prevent overcooling.  Beyond
merely ``sufficient'' feedback, the superbubble model also incorporates physics
that previously have been omitted.  Thermal evaporation is a key process for
mixing cold ISM with hot feedback ejecta.  Prior to \citet{Keller2014}, this
process was completely ignored, and the local mass-loading of feedback was set
purely as a numerical parameter.

As we showed in \citet{Keller2015}, including thermal evaporation in simulations
of a Milky Way like galaxy will drastically change the effectiveness of
SN-driven galactic winds.  Removing gas from the galaxy is the only effective
mechanism for regulating star formation on cosmic timescales.  To prevent the
formation of bulges larger than the ones seen in the local universe, bulge
forming gas (low-angular momentum gas) must be removed from the ISM; because
SN-driven winds are most effective at high redshift, when this material is
mostly accreted, the outflows driven from the galaxy preferentially remove
bulge-forming gas.  An important conclusion of this study is that much of the
past work showing that SN feedback was unable regulate star formation without
the addition of ``early feedback'' from radiation pressure, stellar winds, or
photoionization was likely underestimating the effectiveness of SN.  Since many
of these studies used simpler, more numerically-sensitive feedback models that
also omitted thermal evaporation, they were unable to effectively drive the
correct amount of mass into hot, high entropy gas that could leave the galaxy.
This study tells us that the disc-dominant morphology and low stellar fraction
in galaxies like our own all arise from the same mechanism:  heavily mass
loaded, high redshift winds.

>>>>

\section{Results in Context}
Developing a versatile, accurate, resolution insensitve model for feedback has
been a challenge in galaxy simulations for decades.  While a number of recent
models have been developed that are able to produce galaxies which match some
observables, all of these models have relied on purely numerical features to
enhance the effectiveness of feedback and counter the effects of limited
resolution.  The \citet{Keller2014} presented in Chapter 2 is the first model of
its kind that uses a first-principles approach to prevent overcooling.  Beyond
merely ``sufficient'' feedback, the superbubble model also incorporates physics
that previously have been omitted.  Thermal evaporation is a key process for
mixing cold ISM with hot feedback ejecta.  Prior to \citet{Keller2014}, this
process was completely ignored, and the local mass-loading of feedback was set
purely as a numerical parameter.  \citet{Rosdahl2016} illustrated this clearly,
in a recent comparison project.  This paper implemented 5 popular feedback
algorithms (simple thermal dumps; a delayed cooling model similar to
\citet{Agertz2013}; a kinetic model similar to \citet{DallaVecchia2008}; a
stochastic thermal model based on \citet{DallaVecchia2012}; and a hybrid model
from \citet{Kimm2015}) in the {\sc RAMSES} code.  This allowed for a controlled
test with isolated dwarf and Milky Way analog galaxies. Each of these models,
with ``fiducial'' parameter choices, produced star formation rates that varied
by nearly an order of magnitude in the \citet{Kennicutt1998} star formation
relation.  On top of that, the galaxies showed marked morphological differences
and average wind mass loadings that varied by nearly 4 orders of magnitude.  As
we showed in \citet{Keller2015}, these winds are critical to the formation of
galaxies like the Milky Way.  On top of the inter-model variation,
\citet{Rosdahl2016} also found that the numerical free parameters for each model
had a vast impact on the resulting galaxy star formation rate, morphology, and
outflow properties.  By building a more conservative, physically motivated
model where the local mass loading of supernovae feedback is set by thermal
evaporation, rather than numerically, we can sidestep many of these issues.

The issue of local mass loading has been explored before in simulation.
\citet{Thacker2000} showed a survey of methods for depositing feedback energy.
This work showed that choosing to deposit feedback energy into single resolution
elements vs. smoothing it over an SPH kernel had a significant impact on whether
that feedback energy could couple to the ISM.  \citet{Thacker2000} advocated the
use of a brief adiabatic period, similar to the delayed cooling model presented
in \citet{Rosdahl2016} to prevent overcooling when feedback energy was smoothed.
A more recent study by \citet{DallaVecchia2012} directly looked at the question
of local mass loading with a model that allowed the temperature of post-feedback
gas to be a single tunable parameter.  This is effectively the same as choosing
the amount of mass that each supernovae couples to.  They found that lower mass
loadings result in hotter post-feedback gas, with longer cooling times, and
subsequently much more effective supernovae feedback.  The \citet{Keller2014}
superbubble model is the first model to actually incorporate a physical
mechanism for determining this mechanism.  Previous feedback models have been
designed primarily to avoid the overcooling that can occur when this mass
loading is too high: superbubble feedback instead attempts to calculate the {\it
correct} local mass loadings, and allows the feedback-heated gas to cool with
realistic temperatures and densities.  By building a more physically motivated
model for supernovae feedback, we can have better confidence that results in
simulations testing the effects of this feedback arise from physics rather than
numerics.

As we showed in \citet{Keller2015}, including thermal evaporation in simulations
of a Milky Way like galaxy will drastically change the effectiveness of
SN-driven galactic winds.  Removing gas from the galaxy is the only effective
mechanism for regulating star formation on cosmic timescales.  To prevent the
formation of bulges larger than the ones seen in the local universe, bulge
forming gas (low-angular momentum gas) must be removed from the ISM; because
SN-driven winds are most effective at high redshift, when this material is
mostly accreted, the outflows driven from the galaxy preferentially remove
bulge-forming gas.  A similar result was seen in simulations of dwarf galaxies
by \citet{Brook2011}, but \citet{Keller2015} is the first work to show that
bulgeless disc galaxies similar in mass to the Milky Way can be produced through
the same mechanism, and connect this with the regulation of star formation.  An
important conclusion of this study is that much of the past work
\citet{Stinson2013,Agertz2013,Hopkins2014} showing that SN feedback was unable
regulate star formation without the addition of ``early feedback'' from
radiation pressure, stellar winds, or photoionization was likely underestimating
the effectiveness of SN.  Since many of these studies used simpler, more
numerically-sensitive feedback models that also omitted thermal evaporation,
they were unable to effectively drive the correct amount of mass into hot, high
entropy gas that could leave the galaxy.  This study tells us that the
disc-dominant morphology and low stellar fraction in galaxies like our own all
arise from the same mechanism:  heavily mass loaded, high redshift
winds.

It has been suggested by numerous studies \citep{Benson2003,Bower2006} that AGN
feedback is critical to shaping the galaxy luminosity function.  Most
observations \citep{Kauffmann2003b} show that strong AGN are hosted in galaxies
with halo masses slightly greater than $\sim10^{12}\;M_\odot$.  By simulating a
collection of galaxies that bracket this mass, but omitting the effects of AGN
feedback, we were able to show that SN alone break down as a mechanism of
regulating star formation in these massive galaxies.  Importantly, this also
results in large angular momentum losses for gas within the disc, funneling
material to the central regions where SMBHs reside.  This, combined with the
failure of SN-driven galactic winds, suggests that SN are actually the mechanism
that sets where powerful AGN occur, a mechanism that has begun to be studied in
\citet{Bower2016}.

Chapter 5 presented the first simulation result to reproduce the
\citet{McGaugh2016} RAR.  A later study \citep{Ludlow2016} used data from the
EAGLE \citep{Schaye2015} and APOSTLE \citep{Sawala2016} simulations and
confirmed both the fit to the RAR, and the insensitivity to feedback that we
found.  Earlier, a semi-empirical model was used by \citet{DiCintio2016} showed
that a related observation, the mass-discrepency acceleration relation, could
be produced simply as a result of other pre-existing scaling relations.  Taken
together, these results should seriously temper attempts to fit/explain the RAR
using new, exotic physics.  If conventional baryonic physics produces the same
relation in a $\Lambda CDM$ cosmology, there is little need to turn to modified
gravity \citep{Moffat2016,Verlinde2016} or new forces of nature
\citep{Burrage2016} to explain it.  Precision cosmology has been moving closer
and closer to scales where the effects of baryonic physics are becoming more and
more pronounced.  Without well-constrained subgrid models, like the one
presented here, we will be unable to use the wealth of information available
from galaxies to test new theories of gravity or alternative cosmologies.  On
individual galaxy scales, $\Lambda CDM$ predictions {\it must} include the
details of baryonic effects. Chief among those effects is feedback.
